|

### 2022-10-07 paper_comparison/paper_comparison/paper_comparison.Rmd
fix the p-value calc

```{r}
vi_survey_processed <- readRDS(here::here("data/vi_survey_processed.rds")) 
```

@@

```{r fig:power-poly-uniform, fig.cap = "..."}
vi_survey_processed %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(e_sigma != 0.125) %>%
  mutate(reject_dirichlet = as.numeric(p_value_select_all_plots <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "VI_p_value"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  geom_point(aes(log_effect_size, prop_detect), alpha = 0.3) + geom_point(data = ~filter(.x, unique_lineup_id %in% c("poly_42", "poly_562", "poly_217", "poly_120")), aes(log_effect_size, prop_detect), alpha = 1, col = "red", size = 2) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "VI_p_value"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                filter(x_dist == "uniform") %>%
                pivot_longer(F_p_value:SW_p_value), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  theme_light(base_size = 5) -> p

VI_MODEL$plot_lineup(vi_lineup[["poly_42"]]$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) + 
  ggtitle(bquote(log[e](E) %~~% 2~","~"F-test p-value" == .(format(filter(vi_survey_processed, unique_lineup_id == "poly_42")$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(vi_survey_processed, unique_lineup_id == "poly_42")$p_value_select_all_plots[1], digits = 3)))) -> p1

VI_MODEL$plot_lineup(vi_lineup[["poly_562"]]$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) + 
  ggtitle(bquote(log[e](E) %~~% 3~","~"F-test p-value" == .(format(filter(vi_survey_processed, unique_lineup_id == "poly_562")$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(vi_survey_processed, unique_lineup_id == "poly_562")$p_value_select_all_plots[1], digits = 3)))) -> p2

VI_MODEL$plot_lineup(vi_lineup[["poly_217"]]$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) + 
  ggtitle(bquote(log[e](E) %~~% 4~","~"F-test p-value" == .(format(filter(vi_survey_processed, unique_lineup_id == "poly_217")$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(vi_survey_processed, unique_lineup_id == "poly_217")$p_value_select_all_plots[1], digits = 3)))) -> p3

VI_MODEL$plot_lineup(vi_lineup[["poly_120"]]$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) + 
  ggtitle(bquote(log[e](E) %~~% 2~","~"F-test p-value" == .(format(filter(vi_survey_processed, unique_lineup_id == "poly_120")$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(vi_survey_processed, unique_lineup_id == "poly_120")$p_value_select_all_plots[1], digits = 3)))) -> p4

@@

```{r eval = FALSE}
vi_survey_processed %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(e_sigma != 0.125) %>%
  mutate(reject_dirichlet = as.numeric(p_value_select_all_plots <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
filter(abs(log(effect_size) - 3) < 0.2)

vi_survey_processed %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(e_sigma != 0.125) %>%
  mutate(reject_dirichlet = as.numeric(p_value_select_all_plots <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_abline() +
  geom_point(aes(p_value_uniform, p_value_select_all_plots)) +
  scale_x_log10() +
  scale_y_log10()
```

@@

```{r dist-power, fig.cap="..."}
vi_survey_processed %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(e_sigma != 0.125) %>%
  mutate(reject_dirichlet = as.numeric(p_value_select_all_plots <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "VI_p_value"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  geom_point(aes(log_effect_size, prop_detect), alpha = 0.3) +
  stat_smooth(geom = "line",
              data = ~boot_y(.x, reject_dirichlet, times = 500),
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "VI_p_value"),
              method = "glm",
              method.args = list(family = binomial),
              se = FALSE,
              alpha = 0.03) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                pivot_longer(F_p_value:SW_p_value),
              aes(log_effect_size, as.numeric(value < 0.05), col = name),
              method = "glm",
              method.args = list(family = binomial),
              se = FALSE) +
  facet_wrap(~x_dist) +
  theme_light(base_size = 5)
```

```{r}
vi_survey_processed %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "heteroskedasticity") %>%
  filter(b != 0) %>%
  filter(b < 128) %>%
  mutate(reject_dirichlet = as.numeric(p_value_select_all_plots <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "VI_p_value"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "VI_p_value"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(heter_conv_sim, log_effect_size = log(effect_size)) %>%
                pivot_longer(F_p_value:SW_p_value), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  facet_wrap(~x_dist) +
  ggtitle("heter")
```

>>>>

<!-- TODO:difference between the simple formula and the simulation approach -->

@@

```{r fig:power-poly-uniform, fig.cap = "..."}
vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(e_sigma != 0.125) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "VI_p_value"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  geom_point(aes(log_effect_size, prop_detect), alpha = 0.3) + geom_point(data = ~filter(.x, unique_lineup_id %in% c("poly_502", "poly_78", "poly_6", "poly_447")), aes(log_effect_size, prop_detect), alpha = 1, col = "red", size = 2) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "Visual p-value"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                filter(x_dist == "uniform") %>%
                pivot_longer(F_p_value:SW_p_value), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  theme_light(base_size = 5) -> p

VI_MODEL$plot_lineup(vi_lineup[["poly_502"]]$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) + 
  ggtitle(bquote(log[e](E) %~~% 1~","~"F-test p-value" == .(format(filter(vi_survey, unique_lineup_id == "poly_502")$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(vi_survey, unique_lineup_id == "poly_502")$p_value[1], digits = 3)))) -> p1

VI_MODEL$plot_lineup(vi_lineup[["poly_78"]]$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) + 
  ggtitle(bquote(log[e](E) %~~% 2~","~"F-test p-value" == .(format(filter(vi_survey, unique_lineup_id == "poly_78")$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(vi_survey, unique_lineup_id == "poly_78")$p_value[1], digits = 3)))) -> p2

VI_MODEL$plot_lineup(vi_lineup[["poly_6"]]$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) + 
  ggtitle(bquote(log[e](E) %~~% 3~","~"F-test p-value" == .(format(filter(vi_survey, unique_lineup_id == "poly_6")$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(vi_survey, unique_lineup_id == "poly_6")$p_value[1], digits = 3)))) -> p3

VI_MODEL$plot_lineup(vi_lineup[["poly_447"]]$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(base_size = 5),
                     remove_axis = TRUE) + 
  ggtitle(bquote(log[e](E) %~~% 4~","~"F-test p-value" == .(format(filter(vi_survey, unique_lineup_id == "poly_447")$conventional_p_value[1], digits = 3))~", Visual p-value " == .(format(filter(vi_survey, unique_lineup_id == "poly_447")$p_value[1], digits = 3)))) -> p4

@@

```{r eval = FALSE}
vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(e_sigma != 0.125) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  filter(abs(log(effect_size) - 1) < 0.5) %>%
  filter(n == 100)

vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(e_sigma != 0.125) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_abline() +
  geom_point(aes(p_value_uniform, p_value)) +
  scale_x_log10() +
  scale_y_log10()
```

@@

```{r dist-power, fig.cap="..."}
vi_survey %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(e_sigma != 0.125) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "VI_p_value"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  geom_point(aes(log_effect_size, prop_detect), alpha = 0.3) +
  stat_smooth(geom = "line",
              data = ~boot_y(.x, reject_dirichlet, times = 500),
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "VI_p_value"),
              method = "glm",
              method.args = list(family = binomial),
              se = FALSE,
              alpha = 0.03) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                pivot_longer(F_p_value:SW_p_value),
              aes(log_effect_size, as.numeric(value < 0.05), col = name),
              method = "glm",
              method.args = list(family = binomial),
              se = FALSE) +
  facet_wrap(~x_dist) +
  theme_light(base_size = 5)
```

```{r}
vi_survey %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "heteroskedasticity") %>%
  filter(b != 0) %>%
  filter(b < 128) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "VI_p_value"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "VI_p_value"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(heter_conv_sim, log_effect_size = log(effect_size)) %>%
                pivot_longer(F_p_value:SW_p_value), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  facet_wrap(~x_dist) +
  ggtitle("heter")
```
